### 2020-10-13 README.Rmd
Repo name changes
Final edits

> Pollard, Dominic (2019). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> Pollard, Dominic (2019). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

>>>>

> Pollard, Dominic (2020). _`r Title`_. Name of journal/book, <https://doi.org/xxx/xxx>

@@

> Pollard, Dominic (2020). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### Repository contents

All data, text and code to recreate the paper and analysis therein are found in the 'analysis' folder. Within this, 'analysis/data' contains all raw and derived data, in .csv format. All charts and images from the paper can be found in 'analysis/figures', while the paper itself, and the BibTex file containing all cited works are found in 'analysis/paper'. The folder 'analysis/templates' contains the citation style file, and a template file used to set the style for the Word document produced by 'Family_Fortunes_Article.Rmd'.

@@

> Pollard, Dominic (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
